Supplementary Material for Asymmetry paper

### 2020-05-21 Supplementary/Sup_mat.Rmd
Priors only model run
Priors only model run for the Hoop size experiment

# Power Analysis

@@

```{r run-model-hoop-size-priors, echo = T, cache = TRUE}

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
          data = model_data,
          family = "beta",
          prior = c(set_prior("student_t(3,0,3)", class = "b")),
          cores = 1,
          chains = 1,
          iter = 2000,
          warmup = 1000,
          sample_prior = "only")
```

@@

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
          data = model_data,
          family = "beta",
          prior = c(set_prior("student_t(3,0,3)", class = "b")),
          cores = 1,
          chains = 1,
          iter = 2000,
          warmup = 1000)

>>>>

``` {r}
options(mc.cores = parallel::detectCores())
```
# Power Analysis

@@

```{r run-model-hoop-size-priors, echo = F, include = F, cache = TRUE}

# run model
Hoop_size_priors <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = c(set_prior("student_t(3, 0, 1)",
                                        coef = "norm_hoop_pos",
                                        class = "b"),
                              set_prior("student_t(3,0,1)",
                                        class = "Intercept")),
                    cores = 2,
                    chains = 2,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15),
                    sample_prior = "only")
```

```{r HoopSizePriors, include = T, echo = F, fig.asp = .45, fig.cap="Priors for Hoop size"}
# need to make a dataset
draws <- HS_draw_post(Hoop_size_priors, model_data)

draws$plt_estimates
```

@@

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = c(set_prior("student_t(3,0,1)", class = "b"),
                              set_prior("student_t(3,0,1)", class = "Intercept")),
                    cores = 1,
                    chains = 1,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))
